Bandit Multiclass Linear Classification: \\ Efficient Algorithms for the Separable Case

### 2019-01-23 ICML-submission/mistake-lower-bound-for-ignorant-algorithms.tex
clarification

}
\end{algorithmic}
\end{algorithm}
For this strategy, we prove the mistake lower bound of any ignorant algorithm.
Define the indicators
\begin{align*}
A_t &= \indicator{\forall \tau\le t, p_\tau(1|x_\tau)<1-q_0} \\
B_t &= \indicator{\exists \tau\le t, p_\tau(1|x_\tau)\ge 1-q_0
 \text{\ and\ } \forall s\in[\tau,t), \widehat y_s \neq y_s}.
\end{align*}
Then we have
\begin{align}
& \mathbf{E}\left[\sum_{t=1}^{T} \indicator{\widehat y_t\neq y_t}\right] \nonumber \\
& \ge \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} \indicator{\widehat y_t\neq y_t}\right] \nonumber \\
& \ge \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} \indicator{\widehat y_t\neq y_t}A_t\right] \nonumber \\
& \qquad + \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} \indicator{\widehat y_t\neq y_t}B_t\right] \nonumber \\
& = \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} \mathbf{E}_t\left[\indicator{\widehat y_t\neq y_t}A_t\right]\right] + \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} B_{t+1}\right] \nonumber \\
& \ge \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} q_0 A_t\right] + \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} B_{t+1}\right],
\label{equation:mistake_lower_bound_temp}
\end{align}
where in the first inequality we use $A_t+B_t\le 1$; in the equality, we use
$B_{t+1}=B_t\indicator{\widehat y_t\neq y_t}$ by $B_t$'s definition; in the last
inequality we use the fact that when $t\le N$ and $A_t=1$, it must be $y_t=1$.
Now, denote $T_1 = \argmin_{\tau} \{ p_\tau(1|x_\tau) \ge 1-q_0 \}$ (if such
$\tau$ does not exist or is larger than $\min\{T,N\}$, we simply let
$T_1=\min\{T,N\}+1$). Then $A_t=1$ for all $t\le T_1-1$.

Note that $B_{T_1}=1$, and for $t \ge T_1$ we have
$\Exp[B_{t+1}=0|B_t=1]=\Pr[\widehat y_t=y_t~|~B_t=1] = \Pr[\widehat y_t=2|B_t=1] \le
q_0$ because the algorithm is ignorant. Thus the second term in
\eqref{equation:mistake_lower_bound_temp} can be calculated as

>>>>

}
\end{algorithmic}
\end{algorithm}
For this strategy, we prove the mistake lower bound of any ignorant algorithm.
Define the indicators
\begin{align*}
A_t &= \indicator{\forall \tau\le t, p_\tau(1|x_\tau)<1-q_0} \\
B_t &= \indicator{\exists \tau\le t, p_\tau(1|x_\tau)\ge 1-q_0
 \text{\ and\ } \forall s\in[\tau,t), \widehat y_s \neq y_s}.
\end{align*}
Then we have
\begin{align}
& \mathbf{E}\left[\sum_{t=1}^{T} \indicator{\widehat y_t\neq y_t}\right] \nonumber \\
& \ge \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} \indicator{\widehat y_t\neq y_t}\right] \nonumber \\
& \ge \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} \indicator{\widehat y_t\neq y_t}A_t\right] \nonumber \\
& \qquad + \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} \indicator{\widehat y_t\neq y_t}B_t\right] \nonumber \\
& = \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} \mathbf{E}_t\left[\indicator{\widehat y_t\neq y_t}A_t\right]\right] + \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} B_{t+1}\right] \nonumber \\
& \ge \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} q_0 A_t\right] + \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} B_{t+1}\right],
\label{equation:mistake_lower_bound_temp}
\end{align}
where in the first inequality we use the fact that $A_t$ and $B_t$ cannot be $1$ simultaneously; in the equality, we use
$B_{t+1}=B_t\indicator{\widehat y_t\neq y_t}$ by $B_t$'s definition; in the last
inequality we use the fact that when $t\le N$ and $A_t=1$, it must be $y_t=1$ and $\Pr[\widehat y_t=y_t]=p_t(1|x_t)<1-q_0$.
Now, denote $T_1 = \argmin_{\tau} \{ p_\tau(1|x_\tau) \ge 1-q_0 \}$ (if such
$\tau$ does not exist or is larger than $\min\{T,N\}$, we simply let
$T_1=\min\{T,N\}+1$). Then $A_t=1$ for all $t\le T_1-1$.

Note that $B_{T_1}=1$, and for $t \geq T_1$ the adversary will switch to ``$\textsc{phase}=2$'' and has $y_t=2$. Therefore, 
$\Exp[B_{t+1}=0|B_{t}=1]=\Pr[\widehat y_t=y_t~|~B_t=1] = \Pr[\widehat y_t=2|B_t=1].$ 
Note that when $B_t=1$, by definition there exists a $\tau\le t$ with $p_\tau(1|x_\tau)\ge 1-q_0$, 
and the algorithm all makes mistakes at $\tau, \tau+1, \ldots, t$. Since the algorithm is ignorant, and when $\textsc{phase}=2$, 
the features all remain the same, we have $p_t(1|x_t)=p_{t-1}(1|x_{t-1})=\cdots=p_\tau(1|x_\tau)\ge 1-q_0$. 
Thus we can further upper bound $\Exp[B_{t+1}=0|B_{t}=1]$ by $\Pr[\widehat y_t=2|B_t=1]\leq q_0$. Thus the second term in
\eqref{equation:mistake_lower_bound_temp} can be calculated as
